Ice sheet mass flows

### 2025-08-20 sankey.tex
Remove mass loss/gain arrows. Replace w/ truncated section and label

\begin{tikzpicture}[remember picture, overlay, shift={(5,-5)}]

@@

    \sankeyset{
      %% comment for gray outline
      %% draw/.style={
      %%   draw=white,
      %%   line width=0pt,line cap=round,line join=round,
      %% },
      %% comment for gray outline
      draw/.style={
        draw=black,
        line width=0.1mm,line cap=round,line join=round,
      },
      start style=arrow,end style=arrow,
      %% fill/.style={fill=yellow!10,line width=0pt,draw=yellow!10},
      ratio=1mm/60,
      minimum radius=0mm,
      water/.style={fill/.style={draw=water,line width=0pt,fill=water,},},
      ice/.style={fill/.style={draw=ice,line width=0pt,fill=ice,},},
      air/.style={fill/.style={draw=air,line width=0pt,fill=air,},},
      black/.style={fill/.style={draw=black,line width=0pt,fill=black,},},
      red/.style={fill/.style={fill=none, top color=red, bottom color=red},},
      ice-to-water/.style={fill/.style={fill=none, left color=ice, right color=water},},
      ice-to-air/.style={fill/.style={fill=none, left color=ice, right color=air},},
      ice-to-black/.style={fill/.style={fill=none, left color=ice, right color=black},},
      ice-to-air-vert/.style={fill/.style={fill=none, top color=ice, bottom color=air},},
      ice-to-water-vert/.style={fill/.style={fill=none, bottom color=ice, top color=water},},
      water-to-air-vert/.style={fill/.style={fill=none, right color=water, left color=air},},
      water-to-air/.style={fill/.style={fill=none, left color=water, right color=air},},
      air-to-ice/.style={fill/.style={fill=none, left color=air, right color=ice},},
      red-to-ice/.style={fill/.style={fill=none, left color=red, right color=ice},},
      water-to-ice/.style={fill/.style={fill=none, left color=water, right color=ice},},
      black-to-ice/.style={fill/.style={fill=none, bottom color=ice, top color=black},},
      in-black/.style={draw/.style={draw=gray,thick=3},},
      out-red/.style={draw/.style={draw=red,thick=3},},
      out-blue/.style={draw/.style={draw=water,thick=3},},
      debug label/.style={
        overlay,
        draw,
        font=\tiny,
        text=debug color,text opacity=1,
        inner sep=.1em,
        fill=white,fill opacity=0.5,
        rounded corners=.1em,
        %% node contents={\name: \qty},
        node contents={\qty},
        %% node contents={\name},
      },
    }

@@

    \ifthenelse{\Q{vML} > \Q{vMG}} { % mass loss
      \sankeynode{name=f1, at={[xshift=30mm, yshift=\yoff]SHELFFREEZE.south}, anchor=right,
        quantity=\qq{SMBIN}+\Q{vFRONTADV}+\Q{vSHELFFREEZE}+\Q{vML}+\Q{vRFZ},
        forked={\Q{vRFZ}/RFZi, \Q{vFRONTADV}/FG, \Q{vML}/MLi,
          \qq{SMBIN}/SMBINi, \Q{vSHELFFREEZE}/SHELFFREEZEi}}
    } { % mass gain edge case
      \sankeynode{name=f1, at={[xshift=30mm, yshift=\yoff]SHELFFREEZE.south}, anchor=right,
        quantity=\qq{SMBIN}+\Q{vFRONTADV}+\Q{vSHELFFREEZE}+\Q{vRFZ},
        forked={\Q{vRFZ}/RFZi, \Q{vFRONTADV}/FG, \qq{SMBIN}/SMBINi, \Q{vSHELFFREEZE}/SHELFFREEZEi}}
    }

@@

    \ifthenelse{\Q{vMG} < \Q{vML}} { % mass loss
      \sankeynode{name=ML, quantity=\Q{vML},
        at={[yshift=6mm]RF.north}, anchor=right, angle=-45}
      \node[font=\tiny, anchor=east]
      at ([xshift=-3mm,yshift=2mm]ML.west) {Mass loss: \qq{ML}};

      % frontal advance next to drawdown (mass loss)
      \sankeynode{name=FRONTADVi, quantity=\Q{vFRONTADV},
        at={[yshift=0mm,xshift=6mm]ML.left}, anchor=right, angle=-45}

      \sankeystart[red]{ML}
      \sankeyadvance[red]{ML}{5mm}
      \sankeyoutin[red-to-ice]{ML}{MLi}
    }{ % mass gain
      \sankeynode{name=MGa, quantity=\qq{MG}, angle=-35,
        at={[xshift=5mm,yshift=-3mm]MG.right}, anchor=right}
      \node[font=\tiny, anchor=east]
        at ([yshift=0mm,xshift=0mm]MGa.right) {Mass gain: \qq{MGa}};
      \sankeyoutin[ice-to-black]{MG}{MGa}; \sankeyadvance[black]{MGa}{3mm}
      \sankeyend[black]{MGa}
      \sankeynode{name=FRONTADVi, quantity=\Q{vFRONTADV},
        at={[xshift=-15mm,yshift=8mm]RFZi.right}, anchor=left, angle=-45}
    }

    \ifnum \numexpr\qq{FRONTADVi} > 0
      \sankeystart[in-black]{FRONTADVi}
      \sankeyoutin[in-black]{FRONTADVi}{FG}
      \node[font=\tiny, anchor=east]
          at ([xshift=-3mm,yshift=3mm]FRONTADVi.west) {Frontal advance: \qq{FRONTADVi}};
    \fi

>>>>

\begin{tikzpicture}[remember picture, overlay, shift={(1,-5)}]

@@

    \sankeyset{
      %% comment for gray outline
      %% draw/.style={
      %%   draw=white,
      %%   line width=0pt,line cap=round,line join=round,
      %% },
      %% comment for gray outline
      draw/.style={
        draw=black,
        line width=0.1mm,line cap=round,line join=round,
      },
      start style=arrow,end style=arrow,
      %% fill/.style={fill=yellow!10,line width=0pt,draw=yellow!10},
      ratio=1mm/60,
      minimum radius=0mm,
      water/.style={fill/.style={draw=water,line width=0pt,fill=water,},},
      ice/.style={fill/.style={draw=ice,line width=0pt,fill=ice,},},
      air/.style={fill/.style={draw=air,line width=0pt,fill=air,},},
      black/.style={fill/.style={draw=black,line width=0pt,fill=black,},},
      red/.style={fill/.style={fill=none, top color=red, bottom color=red},},
      ice-to-water/.style={fill/.style={fill=none, left color=ice, right color=water},},
      ice-to-air/.style={fill/.style={fill=none, left color=ice, right color=air},},
      ice-to-black/.style={fill/.style={fill=none, left color=ice, right color=black},},
      ice-to-air-vert/.style={fill/.style={fill=none, top color=ice, bottom color=air},},
      ice-to-water-vert/.style={fill/.style={fill=none, bottom color=ice, top color=water},},
      water-to-air-vert/.style={fill/.style={fill=none, right color=water, left color=air},},
      water-to-air/.style={fill/.style={fill=none, left color=water, right color=air},},
      air-to-ice/.style={fill/.style={fill=none, left color=air, right color=ice},},
      red-to-ice/.style={fill/.style={fill=none, left color=red, right color=ice},},
      water-to-ice/.style={fill/.style={fill=none, left color=water, right color=ice},},
      black-to-ice/.style={fill/.style={fill=none, bottom color=ice, top color=black},},
      in-black/.style={draw/.style={draw=gray,thick=3},},
      out-red/.style={draw/.style={draw=red,thick=3},},
      out-blue/.style={draw/.style={draw=water,thick=3},},
      debug label/.style={
        overlay,
        draw,
        font=\tiny,
        text=debug color,text opacity=1,
        inner sep=.1em,
        fill=white,fill opacity=0.5,
        rounded corners=.1em,
        node contents={\name: \qty},
        %node contents={\qty},
        %% node contents={\name},
      },
    }

@@

    \ifthenelse{\Q{vML} > \Q{vMG}} { % mass loss
      \sankeynode{name=f1, at={[xshift=30mm, yshift=0mm]RFi.north}, anchor=left,
        quantity=\qq{SMBIN}+\Q{vFRONTADV}+\Q{vSHELFFREEZE}+\Q{vML}+\Q{vRFZ},
        forked={\Q{vRFZ}/RFZi, \qq{SMBIN}/SMBINi, \Q{vSHELFFREEZE}/SHELFFREEZEi,
          \Q{vML}/MLi, \Q{vFRONTADV}/FG}}
    } { % mass gain edge case
      \sankeynode{name=f1, at={[xshift=30mm, yshift=0mm]RFi.north}, anchor=left,
        quantity=\qq{SMBIN}+\Q{vFRONTADV}+\Q{vSHELFFREEZE}+\Q{vRFZ},
        forked={\Q{vRFZ}/RFZi, \qq{SMBIN}/SMBINi, \Q{vSHELFFREEZE}/SHELFFREEZEi, \Q{vFRONTADV}/FG}}
    }

@@

    \ifthenelse{\Q{vMG} < \Q{vML}} { % mass loss
      \sankeynode{name=ML, quantity=\Q{vML}, at={[xshift=-15mm,yshift=-\yoff]MLi.south}, anchor=right}
      \sankeyadvance{ML}{1mm} \sankeydubins{ML}{MLi}
      \draw[<-,gray] ([xshift=-2mm]ML.west) -- ++(-10mm,0)
      node[left,font=\tiny,anchor=east,text=black] {Mass loss: \Q{vML}};
    }{ % mass gain
      \sankeyturnleft{MG}{-15} \sankeyadvance{MG}{10mm} % \sankeyturnleft{MG}{15}
      \draw[<-,gray] ([xshift=1mm]MG.east)
      .. controls +(5mm,0) and +(0,0mm) .. ++(5mm,-5mm)
      node[below,font=\tiny,text=black] {Mass gain: \qq{MG}};
    }

    \ifnum \numexpr\Q{vFRONTADV} > 0
      \sankeynode{name=FG0, quantity=\qq{FG}, at={[xshift=-15mm,yshift=-6mm]FG.south}, anchor=right}
      \sankeyadvance{FG0}{1mm} \sankeydubins{FG0}{FG}

      \draw[<-,gray] ([xshift=-2mm]FG0.west) -- ++(-10mm,0)
      node[left,font=\tiny,anchor=east,text=black] {Frontal advance: \qq{FG}};
    \fi
